\documentclass{amsart}

\usepackage{amsmath, amssymb}

\begin{document}

\title{Sample Final Exam for ``Set Theory and Logic Throughout Mathematics"}
\maketitle

You have up to 30 minutes to complete the exam. Take up to 15 minutes to decide 
on a topic and prepare your answers, and then use the remainder of the time to 
present your answers. You may not use outside sources/materials during the exam.
If you have any questions/need any clarification, please feel free to ask.

\bigskip

Choose either (A) or (B), and answer all parts included therein.

\bigskip

\noindent \textbf{(A)} (Zorn's Lemma)

\smallskip

(1) Define ``partial order", and give some natural examples of partial orders.

\smallskip

(2) State Zorn's Lemma.

\smallskip

(3) Give at least one other principle that is equivalent to Zorn's Lemma over the axioms of $\mathsf{ZF}$.

\smallskip

(4) Describe an application of Zorn's Lemma, including a basic outline of the proof of the result.

\bigskip

\noindent \textbf{(B)} (Categoricity of algebraically closed fields)

\smallskip

(1) Define ``field", ``characteristic of a field", and ``algebraically closed field".

\smallskip

(2) Given a cardinal $\kappa$, describe what it means for a first-order theory $T$ to be 
``$\kappa$-categorical".

\smallskip

(3) Give a broad outline of the proof of the fact that the theory of algebraically closed fields 
of a fixed characteristic is $\kappa$-categorical for every uncountable cardinal $\kappa$.

\smallskip

(4) Explain why the theory of algebraically closed fields of a fixed characteristic is not 
$\aleph_0$-categorical.


\end{document}